Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-06 thesis/paper.tex
Review disc RQ1.1

\noindent
\textbf{Functionality is reverse engineerable  } 
All changes which main motivation were to either add or remove functionality were accurately predicted. These changes were the most major ones, and it was expressed during the interview that these changes were the main motive behind the introduction of the new version. In summary, 11 out of a total 13 changes were correctly predicted. It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted. This supports that such changes have a clearer intent and are perhaps more well-defined.

\smallskip \noindent
\textbf{``Structural'' changes are not reverse engineerable  }
3 out of 5 changes which did not add functionality, but rather were introduced to redcue complexity and increase quality were correctly predicted. The two changes which were not predicted correctly were wrong because the main-motivation was mixed up with the sub-intention (!!!re-phrase). This shows that although the prediction was incorrect, the general reasoning was correct. Our predictions were accurate enough to allow us to form a reliable conlusion which created a good means for discussion with the company (!!!re-phrase).

>>>>

\noindent
\textbf{Functionality is reverse engineerable  } %Reviewed by W
All changes which main motive were to either add or remove functionality were accurately predicted. These changes were the most major ones, and it was expressed during the interview that these types of changes main driving factor behind the development of the new version. In summary, 11 out of a total 13 changes were correctly predicted. It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted. This supports that such changes have a clearer intent and are perhaps more well-defined.

\smallskip \noindent
\textbf{``Structural'' reverse engineerable to a lesser extent} %Reviewed by W
3 out of 5 changes which did not add functionality, but rather were introduced to redcue complexity and increase quality were correctly predicted. The two changes which were incorrectly predicted were wrong because the main motivation was mixed up with the secondary intent ( "re-phrase"). This shows that although the prediction was incorrect, the general reasoning was correct. Our predictions were accurate enough to allow us to form a reliable conlusion which created a good means for discussion with the company ( "re-phrase").
